---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# studious

<!-- badges: start -->
<!-- badges: end -->

This package is an active work in progress. 
The goal of studious is to be a simple tool that helps students that are new to R as it was born out of my reflections on my own learning journey as a masters student in statistics. This package will contain code that to generate basic study guides, homework templates, and presentation templates using Quarto documents.

## Installation

You can install the development version of studious from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("mkmckellar/studious")
```

## Example

This is a basic example on how you generate a study guide as an HTML document. 

```{r example, eval = FALSE}
library(studious)
## basic example code

create_homework_html(file_name = "class101_homework1",
                     your_name = "Riley Pupil")
```
